---
output: 
  github_document:
    toc: TRUE
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "50%"
)
options(tidyverse.quiet = TRUE)

package_exists <- F
print_reports <- F
build_package <- F
build_package_w_readme <- F

print_reports_action <- ifelse(print_reports, "asis", "hide")
```

# {vizbroom}



## Installation

You can install the development version of vizbroom from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("EvaMaeRey/vizbroom")
```

## User interface idea... 



```{r example, eval = package_exists}
library(ggplot2) 
library(ggbroom)

visbroom(data = ?, formula = ?, method = ?) + 
  viz_glance()

visbroom(data = ?, formula = ?, method = ?) + 
  viz_tidy()

visbroom(data = ?, formula = ?, method = ?) + 
  viz_tidy_stdz()

visbroom(data = ?, formula = ?, method = ? ) + 
  viz_augment()

visbroom(data = ?, formula = ?, method = ? ) + 
  viz_augment_stdz()
```



```{r}
```

 



<!-- badges: start -->
<!-- badges: end -->

# How we built this functionality



## Step 0. Build vis with base ggplot2 and broom



```{r}
library(broom)
# glance
# augment
# tidy
stdz <- function(x){
  
  (x - mean(x))/sd(x)
  
}

m <- lm(dist ~ speed, data = cars)





glance(m) 
tidy(m)
augment(m) |> head()


library(ggplot2)
library(magrittr)

glance(m) %>%  
  tidyr::pivot_longer(cols = 1:length(.)) %>% 
  dplyr::mutate(which = dplyr::row_number()) %>% 
ggplot(data = .) + 
  aes(x = 0, y = which) + 
  geom_text(aes(label = name), hjust = 0 ) + 
  geom_text(aes(label = value, x = 1), hjust = 1)

tidy(m) |>
  ggplot() + 
  aes(y = term, x = estimate) + 
  geom_point() + 
  geom_segment(aes(x = estimate + std.error,
                   xend = estimate - std.error,
                   yend = term))

lm(stdz(dist) ~ stdz(speed), data = cars) |>
 tidy() |>
  ggplot() + 
  aes(y = term, x = estimate) + 
  geom_point() + 
  geom_segment(aes(x = estimate + std.error,
                   xend = estimate - std.error,
                   yend = term))


ggplot(data = augment(m)) + 
  aes(x = speed, y = dist) + 
  geom_point() + 
  geom_point(aes(y = .fitted), color = "blue")



```



# Write functions w/ 'recipe' substeps: 1. compute_?; 2. define ggproto; 3. write geom_*; 4. test.

## Write `geom_county()` (polygon)

```{r geom_county}
################# Step 1. Compute panel function ###########

###### Step 2. Specify ggproto ###############

########### Step 3. geom function, inherits from sf ##################


```


## try it out..

```{r}

```



```{r, echo = F}
if(!build_package_w_readme){knitr::knit_exit()}
```

# Part 2. Packaging and documentation  🚧 ✅ 

## minimal requirements for github package.  Have you:

### Created files for package archetecture with `devtools::create("./ggbarlabs")` ✅ 

### Moved functions R folder? ✅  



```{r}
library(readme2pkg)
chunk_to_r("data")
chunk_to_r("geom_county")
chunk_to_r("geom_county_labels")
chunk_to_r("stamp_county")
chunk_to_r("stamp_roads")
```


### Added roxygen skeleton? ✅ 

 for auto documentation and making sure proposed functions are *exported*

### Managed dependencies ? ✅ 

package dependencies managed, i.e. `depend::function()` in proposed functions and declared in the DESCRIPTION

### Chosen a license? ✅ 


```{r, eval = F}
usethis::use_package("ggplot2")
usethis::use_mit_license()
```

### Run `devtools::check()` and addressed errors? ✅ 


## Listen 🚧 

### Consulted with potential users 🚧 
### Consulted with technical experts 

Getting started with that!

## Polish.  Have you...

### Settled on examples and put them in the roxygen skeleton? 🚧 

### Written formal tests of functions? 🚧 


### Sent tests in this readme to package via readme2pkg 🚧 

That would look like this...

```
chunk_to_tests_testthat("test_geom_barlab_count")
```


### Have you worked added a description and author information in the DESCRIPTION file? 🚧 

### Addressed *all* notes, warnings and errors. 🚧 

## Promote

### Package website built? 🚧 

### Package website deployed? 🚧 

## Harden

### Submit to CRAN?  🚧 


# Reports, Environment

## Description file extract

```{r}

```

## Environment

Here I just want to print the packages and the versions

```{r}
all <- sessionInfo() |> print() |> capture.output()
all[11:17]


```

## `devtools::check()` report

```{r, error = T, results = print_reports_action}
# rm(list = c("geom_barlab_count", "geom_barlab_count_percent"))
devtools::check(pkg = ".")
```





# Install development package with `devtools::build()`

```{r, error = T, eval = build_package, results = print_reports_action}
devtools::build()
```



## Repo Directory and files report

Let's look at the repository contents. 

```{r}
fs::dir_tree(recurse = T)
```












#############

### Changing context

Here is a suggested preparation for a package for allowing for ggbrasilstates easy creation of brazilian state choropleth, reading in an sf states object from the geombr package.

```
brasil_state_sf <- geobr::read_state() %>%
  rename(state_code = code_state,
         state_abb = abbrev_state,
         state = name_state,
         region_code = code_region,
         region = name_region,
         geometry = geom)# year 2010
```         

Then a number of changes would need to be made to update the DATASET.R file, including object names.  Also notably there are quite a few columns that are ID columns compared to the North Carolina case. 

Find and change can be used for object name changes.

```
id_cols = c(county_name, fips) -> id_cols = c(state_code, state_abb, state, region_code, region)
county -> state
northcarolina -> brasil
```


For ggbrasil in these files changes should be made:

```
County -> State
```

New examples should be crafted.
